Report - Latest Rodent Data

### 2017-12-01 evaluation.Rmd
Fix paths in site files, delete temporary files after forecastall

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(portalr)
source("forecast_tools.R")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(portalr)
source("tools/forecast_tools.R")
```

### 2017-12-01 index.Rmd
Fix paths in site files, delete temporary files after forecastall

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(portalr)
source("forecast_tools.R")
```

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(portalr)
source("tools/forecast_tools.R")
```

@@

```{r speciesforecasts, echo=FALSE, message=FALSE, warning=FALSE}
source("tools/forecast_tools.R")

### 2017-12-01 report.Rmd
Fix paths in site files, delete temporary files after forecastall

---
title: "Report - Latest Rodent Data"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("forecast_tools.R")
library(portalr)

@@

# get most recent forecast prior to data collection
files = data.frame(names = list.files(path = './predictions', pattern = '*Allforecasts.csv'))
files$filedates = as.Date(substr(files$names,1,10),format='%Y-%m-%d')
latest_forecast = dplyr::filter(files,filedates<most_recent_date) %>% tail(1)

>>>>

---
title: "Report - Latest Rodent Data"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("tools/forecast_tools.R")
library(portalr)

@@

# get most recent forecast prior to data collection
files = data.frame(names = list.files(path = './predictions', pattern = '*forecasts.csv'))
files$filedates = as.Date(substr(files$names,1,10),format='%Y-%m-%d')
latest_forecast = dplyr::filter(files,filedates<most_recent_date) %>% tail(1)
